Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-10 paper/structureScene.tex
better line widths in Fig 1
add script figure generation supervised, update figures unsupervised (final results)

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\begin{figure}
\begin{center}
\setlength{\unitlength}{1cm}
\begin{picture}(5,2)
 \put(-1.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q8.png}}
 \put(2.5,0.0){\includegraphics[height=2cm,width=3.5cm]{gammatone_Q1.png}}
\end{picture}
\caption{
\label{fig:gammatones}
Left: Gammatone wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$ with a quality factor of $Q_1=8$.
Right: Gammatone wavelet $\boldsymbol{\psi_{\gamma_2}}(t)$ with a quality factor of $Q_2=1$.
\vl{we should discuss color schemes and axis labels} \ml{yes we should but for the second submission, go ahead}}
\end{center}
\end{figure}

@@

\subsection{Standardization}
Let $\mathbf{S}\boldsymbol{X}(\gamma,n)$ be a dataset, where the indices $\gamma$ and $n$ respectively denotes features and examples.
It is commonly acknowledged that support vector machines should be trained on scaled features with null mean and unit variance, so as to avoid mismatch in numeric ranges.
This operation may also help making the dataset linearly separable in feature space.
\vl{Check this claim in DCASE 2013 time scattering features.}
To standardize $\mathbf{S}\boldsymbol{X}(\gamma,n)$, we apply the affine transformation
\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{ \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma)}{\sigma[ \mathbf{S}\boldsymbol{X}](\gamma)}
\end{equation}
where $\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma) = \frac{1}{N} \sum_{n=1}^{N} \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the expected value of $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma[\mathbf{S}\boldsymbol{X}] (\gamma) =
\sqrt{\frac{1}{N-1} \sum_{n=1}^{N}
\left( \mathbf{S}\boldsymbol{X}(\gamma,n) - \mathbb{E}[\mathbf{S}\boldsymbol{X}] \right)^2}
\end{equation}
 is the sample standard deviation.

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pgf}
%\usepackage{tikz}
%\usetikzlibrary{arrows,positioning}
%\usetikzlibrary{arrows.meta}
\usepackage{url}
\usepackage{color}
\usepackage{graphicx}
\usepackage{xspace}
\newcommand*{\eg}{e.g.\@\xspace}
\newcommand*{\ie}{i.e.\@\xspace}
\newcommand*{\vs}{vs.\@\xspace}

% correct bad hyphenation here
\hyphenation{wave-let}

@@

%\begin{figure}
%\begin{center}
%\begin{tikzpicture}
%\useasboundingbox[red] (-0.25, -0.5) rectangle (8.25, 2);
%\node (omlabel1) at (3.5, 1) {$t$};
%\draw[-{Latex[length=2mm]}] (0, 1) -- (omlabel1);
%\draw[-{Latex[length=2mm]}] (0, 1) -- (0, 2);
%\node[anchor=south west,inner sep=0] at (0, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q8.png}};
%\node at (2, -0.25) {(a)};
%\node (omlabel2) at (8, 1) {$t$};
%\draw[-{Latex[length=2mm]}] (4.5, 1) -- (omlabel2);
%\draw[-{Latex[length=2mm]}] (4.5, 1) -- (4.5, 2);
%\node[anchor=south west,inner sep=0] at (4.5, 0) {\includegraphics[height=2cm,width=3cm]{gammatone_Q1.png}};
%\node at (6.5, -0.25) {(b)};
%\end{tikzpicture}
%\caption{
%\label{fig:gammatones}
%Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$. Blue and red oscillations represent the real and imaginary parts. The orange envelope represents the complex modulus.}
%\end{center}
%\end{figure}

@@

\subsection{Standardization}
Let $\mathbf{S}\boldsymbol{X}(\gamma,n)$ be a dataset, where the indices $\gamma$ and $n$ respectively denotes features and examples.
It is commonly acknowledged that support vector machines should be trained on scaled features with null mean and unit variance, so as to avoid mismatch in numeric ranges.
This operation may also help making the dataset linearly separable in feature space.
To standardize $\mathbf{S}\boldsymbol{X}(\gamma,n)$, we apply the affine transformation
\begin{equation}
\widetilde{\mathbf{S}}\boldsymbol{X}(\gamma, n) =
\dfrac{ \mathbf{S}\boldsymbol{X}(\gamma, n) -
\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma)}{\sigma[ \mathbf{S}\boldsymbol{X}](\gamma)}
\end{equation}
where $\mathbb{E}[ \mathbf{S}\boldsymbol{X}](\gamma) = \frac{1}{N} \sum_{n=1}^{N} \mathbf{S}\boldsymbol{X}(\gamma,n)$ is the expected value of $\mathbf{S}\boldsymbol{X}(\gamma,n)$ and
\begin{equation}
\sigma[\mathbf{S}\boldsymbol{X}] (\gamma) =
\sqrt{\frac{1}{N-1} \sum_{n=1}^{N}
\left( \mathbf{S}\boldsymbol{X}(\gamma,n) - \mathbb{E}[\mathbf{S}\boldsymbol{X}] \right)^2}
\end{equation}
 is the sample standard deviation.
